Weighted Model Counting with Conditional Probabilities

### 2020-07-01 paper.tex
Add weights to the Ace encodings

\paragraph{Experimental setup.}
\begin{itemize}
\item
  Algorithms\footnote{\url{http://beyondnp.org/pages/solvers/model-counters-exact/}}
  (highlighted the initial setup, can expand later):
  \begin{itemize}
  \item \hl{ADDMC} \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
    multiplicativity of BAs in different words) (with optimal settings)
  \item Cachet \cite{DBLP:conf/sat/SangBBKP04}
  \item c2d \cite{DBLP:conf/ecai/Darwiche04}
  \item d4 \cite{DBLP:conf/ijcai/LagniezM17} (closed source, boo!)
  \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
  \end{itemize}
\item Encodings:
  \begin{itemize}
  \item \texttt{-d02} \cite{DBLP:conf/kr/Darwiche02}
  \item \texttt{-sbk05} \cite{DBLP:conf/aaai/SangBK05}
  \item \texttt{-cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
  \item \texttt{-cd06} \cite{DBLP:conf/sat/ChaviraD06} (supposed to be the best)
  \item mine
  \end{itemize}
  All except mine are from Ace
  3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and should be compiled
  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
  \texttt{-noEclause} (i.e., only use standard syntax) flags. Ace also has its
  own benchmarks (with evidence) but they're still binary.
\item Datasets\footnote{There might be more at
    \url{https://meelgroup.github.io/}.}
  \begin{itemize}
  \item binary Bayesian networks from Sang et
    al.\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}
    \cite{DBLP:conf/aaai/SangBK05}
    \begin{itemize}
    \item \hl{Grid networks}: computing marginal probability of the last node in
      the grid (DNE).
    \item Plan recognition problems (DNE + XML).
    \item Deterministic quick medical reference (DNE + XML).
    \end{itemize}
    For the last two, the task can be to calculate the marginal probability of a
    randomly chosen node (so, repeat at least ten times).
  \item Bayesian networks \emph{with evidence} (some binary, some non-binary)
    \begin{itemize}
    \item \texttt{2004-pgm}: NET + inst (\cite{DBLP:journals/ijar/ChaviraDJ06})
    \item \texttt{2005-ijcai}: XDSL/NET/Hugin + inst (\cite{DBLP:conf/ijcai/ChaviraD05})
    \item \texttt{2006-ijar}: NET + inst (\cite{DBLP:journals/ijar/ChaviraDJ06})
    \end{itemize}
  \item ProbLog \cite{DBLP:conf/uai/FierensBTGR11}
  \item probabilistic programs \cite{DBLP:journals/corr/abs-2005-09089}
  \end{itemize}
\end{itemize}

>>>>

\paragraph{Experimental setup.}
\begin{itemize}
\item
  Algorithms\footnote{\url{http://beyondnp.org/pages/solvers/model-counters-exact/}}
  (highlighted the initial setup, can expand later):
  \begin{itemize}
  \item ADDMC \cite{DBLP:conf/aaai/DudekPV20} (rediscovered the
    multiplicativity of BAs in different words) (with optimal settings)
  \item Cachet \cite{DBLP:conf/sat/SangBBKP04}
  \item c2d \cite{DBLP:conf/ecai/Darwiche04}
  \item d4 \cite{DBLP:conf/ijcai/LagniezM17} (closed source, boo!)
  \item miniC2D  \cite{DBLP:conf/ijcai/OztokD15}
  \end{itemize}
\item Encodings:
  \begin{itemize}
  \item \texttt{-d02} \cite{DBLP:conf/kr/Darwiche02}
  \item \texttt{-sbk05} \cite{DBLP:conf/aaai/SangBK05}
  \item \texttt{-cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
  \item \texttt{-cd06} \cite{DBLP:conf/sat/ChaviraD06} (supposed to be the best)
  \item mine
  \end{itemize}
  All except mine are from Ace
  3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and should be compiled
  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
  \texttt{-noEclause} (i.e., only use standard syntax) flags. Ace also has its
  own benchmarks (with evidence) but they're still binary.
\item Datasets\footnote{There might be more at
    \url{https://meelgroup.github.io/}.}
  \begin{itemize}
  \item binary Bayesian networks from Sang et
    al.\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}
    \cite{DBLP:conf/aaai/SangBK05}
    \begin{itemize}
    \item Grid networks: computing marginal probability of the last node in
      the grid (DNE).
    \item Plan recognition problems (DNE + inst).
    \item Deterministic quick medical reference (DNE + inst).
    \end{itemize}
    For the last two, the task can be to calculate the marginal probability of a
    randomly chosen node (so, repeat at least ten times).
  \item Bayesian networks available with Ace (some binary, some non-binary)
    \begin{itemize}
    \item \texttt{2004-pgm}: NET + inst (\cite{DBLP:journals/ijar/ChaviraDJ06})
    \item \texttt{2005-ijcai}: XDSL/NET/Hugin + inst (\cite{DBLP:conf/ijcai/ChaviraD05})
    \item \texttt{2006-ijar}: NET + inst (\cite{DBLP:journals/ijar/ChaviraDJ06})
    \end{itemize}
  \item ProbLog \cite{DBLP:conf/uai/FierensBTGR11}
  \item probabilistic programs \cite{DBLP:journals/corr/abs-2005-09089}
  \end{itemize}
\end{itemize}
